Uncertainty in social learning evolution

### 2022-05-17 ms.tex
updated model dynamics fig and caption

\title{Uncertainty in the evolution of social learning}

@@

\begin{figure}
  \caption{Model dynamics are composed of two major parts: first, agents perform
  behaviors for $L$ time steps in a single generation. Then agents reproduce
  randomly, with more successful agents being more likely to reproduce. Newly
  ``born'' social learner agents use success bias to select and learn from a chosen
  teacher. Then, all agents from the previous generation die off, all new agents
  begin a new generation, and the process continues until 1000 total time steps
  have elapsed. Agents are initialized as ``blank slates''. \mt{Can compress this
  into triptych. $M \rightarrow L$. Lighten grey background, remove outlines
around most or all components. Replace text in picture with A, B, C, and 
explain in caption.}}
  \label{fig:IntraInterGenerationalDynamics}
  \centering
    \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
\end{figure}

>>>>

\title{Uncertainty in social learning evolution}

@@

\begin{figure}
  \caption{\textbf{Model dynamics.} 
    The first generation of agents are initialized with empty ledgers, 
    then perform behaviors on each subsequent time step (A). At the end
    of each generation, after all agents have performed $L$ behaviors
    chosen using softmax selection, the intergenerational tramsission stage
    begins (B). During this stage agents reproduce, passing on their social
    learning trait without mutation (B1). Child agents learn from
    the previous generation if they are social learners (B2), or are initialized
    with blank ledgers if they are individual learners. All agents from the previous
    generation die off, and new child agents begin within-generation dynamics anew.}
  \label{fig:IntraInterGenerationalDynamics}
\hspace{-2em}
  % \centering 
    \includegraphics[width=1.1\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
\end{figure}
